Log Journal Project Theme 9

### 2022-10-13 Resources/LogJournal.Rmd
Finishes the logjournal

>>>>

RandomForest has seven attributes. Below is a table with each attribute and its meaning.

```{r, echo=FALSE}
attr <- c("P", "I", "num-slots", "K", "M", "V", "S")
attr.descr <- c("Size of each bag, as a percentage of the training set size.", 
                "Number of iterations.", "Number of execution slots.", 
                "Number of attributes to randomly investigate.", 
                "Number of attributes to randomly investigate.", 
                "Set minimum numeric class variance proportion.", 
                "Seed for random number generator.")
pander(data.frame(Attribute=attr, Description=attr.descr))
```

Weka will find the optimal parameters for a classifier. With CVParameterSelection in Weka were the best parameters found.

```{r, echo=FALSE}
old.val <- c(100, 100, 1, 0, 1, 0.001, 1)
new.val <- c(50, 1000, 0, 1, 1, 0.001, 1)
pander(data.frame(Attribute=attr, Old.Values=old.val, New.Values=new.val))
```

This table shows the parameters with their default settings and their new. P, I, num-slots and K were different than the default settings. The build will take more time because it does 10 times more I(terations).

![Iterations ranked]("images/WekaIterRank.png")

Number 1 in the figure above is with 1000 I(terations) and number 2 is 100 I(terations). And there is not a significant difference. So for performance, the value for I will be 100.

Weka Meta learners were used to get a better idea of an optimal classifier.

```{r, echo=FALSE}
tbl <- read.table("MetaResults.txt", header = TRUE)
colnames(tbl) <- c("Classifier", "TP Rate", "FP Rate", "Precision", "ROC Area", " ")
pander(tbl)
```

As it can be seen in this table, RandomForest with tweaked parameters is the best. This one has no ? at VAC and precision.

Since there are 10 classifications, ROC curve have been caught from one classifications.

![ROC Curve (NUC)]("images/ROCCurve.png")

This is a nice curve with a relative low ROC Curve. This means that this classification can correspond well to a particular decision threshold.
